The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
minor changes to the paper

The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.  Indeed, it first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.

@@

The last option we describe for {\tt nu} is {\tt IsLocal}.
Notice that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n>0$ for which $(I^n)^{[1/p^e]} \not\subseteq \idealm$.
When computing its value globally, it is the maximum $n>0$ for which $(I^n)^{[1/p^e]} \neq R$, and when 
the value of {\tt IsLocal} is set to {\tt false} (from its default {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and instead calculates determines this value $n$.

\[
\min_{J \in \mathfrak{m}-\Spec R} \nu_I^J(p^e)
\]
% This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it 
by determining the values $n$ for which $(I^n)^{[1/p^e]}$ is a unit ideal.

@@

The general method applied calls upon functionality from the \emph{TestIdeals} package \cite{TestIdealsPackage, TestIdealsPaper}.  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small. For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
$\tau(R, f^{t-\varepsilon})$ is not.
(Note that for $R$ strongly $F$-regular and Gorenstein, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.)
%These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.

>>>>

The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.  Indeed, it first appeared in the work
of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.

@@

The last option we describe for {\tt nu} is {\tt IsLocal}.
Notice that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]} \neq R$, and when 
the value of {\tt IsLocal} is set to {\tt false} (from its default value {\tt true}), then {\tt nu} instead determines this value $n$.  Note that this value is also the minimum $\nu_I^\mathfrak{n}(p^e)$ among all maximal ideals $\mathfrak{n}$ of $R$.

% 
% \[
% \min_{J \in \mathfrak{m}-\Spec R} \nu_I^J(p^e)
% \]
% This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it 
%by determining the values $n$ for which $(I^n)^{[1/p^e]}$ is a unit ideal.

@@

The general method applied calls upon functionality from the \emph{TestIdeals} package.  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small. For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
$\tau(R, f^{t-\varepsilon})$ is not.
Note that for $R$ strongly $F$-regular and Gorenstein, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
